Meta-analysis

### 2021-02-24 04_MetaAnalysis.Rmd
summarise the division of spray shedules under each disease pressure

```{r}
anova(PM_mv, PM_mv_dp)
```
This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value.
However the higher AIC indicates that the model omitting `d_pressure` is a slightly better fit.
Also the chi-squared test uncertain that the `d_pressure` model is significantly better as indicated by the `pval` 0.1336.
The higher log likelihood on the `d_pressure` model does intricate there is some merit to this model and that perhaps with more trials to increase statistical power might provide a useful model.

>>>>

```{r}
anova(PM_mv, PM_mv_dp)
```
This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value.
However the higher AIC indicates that the model omitting `d_pressure` is a slightly better fit.
Also the chi-squared test marginally significant that the `d_pressure` model is better as indicated by the `pval` 0.0468.
The higher log likelihood on the `d_pressure` model does indicate there is some merit to this model.  
It is worth noting that there were no Late plus schedules that experienced low disease pressure. 
Even though the disease pressure interaction on the moderators was marginally significant (P =0.0468), the division of schedules due to disease pressure (reducing k) makes drawing conclusions risky. More data is needed to explore this possible effect.

```{r}
PM_dat_Y %>%
   group_by(spray_management, d_pressure)%>%
   summarise(n())
```
